\LARGE \bf Expectation-Maximization based defense mechanism for distributed Model Predictive Control

### 2022-05-09 article/article.tex
v needs to be linear at least

The \emph{local problems}~\eqref{eq:DOP_local} can be rewritten in a equivalent (same solution) constrained \qp{} form:
  \begin{subequations}\label{eq:quadratic_case}
    \begin{align}
      \label{eq:4}
      \underset{\Uik}{\mathrm{minimize}}&&\small J_{i}(\vec{\theta}_{i})=&\frac{1}{2} \Uik^T H_i\Uik +{\fik}^T\Uik\\
      \mathrm{subject~ to}&&&\bar{\Gamma}_{i}\Uik\preceq\vec{\theta}_{i}[k]:\vec{\lambda}_{i}[k]\label{eq:constraints}\\
                                        &&&\Uik\succeq\0_{c},
    \end{align}
  \end{subequations}
where ${\Uik}$ stacks the input prediction sequences, and
${\bar{\Gamma}_{i}=\kron{I_{\predhorz}}{\Gamma_{i}}}$.
The values for $H_{i}$ and $\vec{f}_{i}[k]$ vary depending on the control objective $\vec{v}_{i}[k]$. The approach presented in this paper does not depend on the choice of the control objective.
The approach depends only on the fact that ${H_{i}\in\semidefpos}$ does not depend on $k$, while $\fik$ does. Those facts are instrumental for the results in the following sections.

>>>>

The \emph{local problems}~\eqref{eq:DOP_local} can be rewritten in a equivalent (same solution) constrained \qp{} form:
  \begin{subequations}\label{eq:quadratic_case}
    \begin{align}
      \label{eq:4}
      \underset{\Uik}{\mathrm{minimize}}&&\small J_{i}(\vec{\theta}_{i})=&\frac{1}{2} \Uik^T H_i\Uik +{\fik}^T\Uik\\
      \mathrm{subject~ to}&&&\bar{\Gamma}_{i}\Uik\preceq\vec{\theta}_{i}[k]:\vec{\lambda}_{i}[k]\label{eq:constraints}\\
                                        &&&\Uik\succeq\0_{c},
    \end{align}
  \end{subequations}
where ${\Uik}$ stacks the input prediction sequences, and
${\bar{\Gamma}_{i}=\kron{I_{\predhorz}}{\Gamma_{i}}}$.
The values for $H_{i}$ and $\vec{f}_{i}[k]$ vary depending on the control objective $\vec{v}_{i}[k]$.
The approach presented in this paper works for linear control objectives such as ${\vec{v}_{i}[k]=\vec{y}_{i}[k]}$ and ${\vec{v}_{i}[k]=\vec{y}_{i}[k]-\vec{w}_{i}[k]}$.
The approach depends only on the fact that ${H_{i}\in\semidefpos}$ does not vary w.r.t. $k$, while $\fik$ does. Those facts are instrumental for the results in the following sections.
